\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
\usepackage{sectsty}
\sectionfont{\fontsize{12}{10}\selectfont}
\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{2.8ex plus 1ex minus .2ex}{0pt}

\begin{document}
    \begin{center}
        \Title{Pranav P}
        
        \begin{SubTitle}
        Assariparambil, CMC 11, Cherthala P.O, Alappuzha, 688524 \\
        \href{mailto:pranavsdreams@gmail.com} {pranavsdreams@gmail.com}
        | +91 8301871729
        | \href{https://github.com/pranavkaruvally} {\url{github.com/pranavkaruvally}} 
        | \href{https://www.linkedin.com/in/pranav-p-76b901183} {LinkedIn: pranav p}
        \end{SubTitle}
    \end{center}

    \section*{EDUCATION}
        % \vspace{5pt}
        % \textbf{\large EDUCATION}
        % \vspace{5pt}
        \hrule
        \vspace{8pt}
        {\href{https://cet.ac.in}{\textbf{\large College of Engineering Trivandrum}},
        {\large Kerala India}  
        \newline\textit{\large Master of Computer Applications}}
        \hfill
        Expected \DatestampYMD{2024}{06}{01}
        \vspace{5pt}

        {\href{https://cmscollege.ac.in}{\textbf{\large CMS College Kottayam}},
        {\large Kerala India}
        \newline\textit{\large BSc. Mathematics}
        \newline Cumulative GPA: 9.06}
        \hfill
        \DatestampYMD{2019}{06}{10} --
        \DatestampYMD{2022}{04}{01}
        \vspace{5pt}

        {\textbf{\large Holy Family HSS Cherthala}
        \newline\textit{\large Plus Two (PCMC)}
        \newline Score: 98.5\%}
        \hfill
        \DatestampYMD{2017}{06}{01} --
        \DatestampYMD{2019}{03}{31}

    \section*{INTERNSHIPS}
        \hrule \vspace{8pt}
        {\href{https://fossee.in}{\textbf{\large FOSSEE, IIT Bombay}}
        \newline\textit{\large Semester long Internship 2023}
        }
        \hfill
        {\DatestampYMD{2023}{02}{14} --
        \DatestampYMD{2023}{07}{14}}
        \BulletItem
            Selected as one of the only two candidates through a screening task.
            \newline Result: \href{https://fossee.in/semester-internship/2023/results}{https://fossee.in/semester-internship/2023/results}
        \BulletItem
            Added four new features in eSim(an open source EDA) developed by the FOSSEE eSim team at IIT Bombay under\newline the mentorship of project assistants Sumanto Kar and Rahul Pakniker.
        \BulletItem
            Suppressed output graphs automatically generated by ngspice during simulation and added GUI elements using PyQt.
        \BulletItem
            Implemented multithreading using slots and signals to prevent the PyQt event loop from sleeping allowing two or more tasks to be done during simulation simultaneously.

    \section*{PROJECTS}
        \hrule \vspace{8pt}
        {\href{https://github.com/pranavkaruvally/linux_package_management_system}
        {\textbf{\large GUI for Verilator}} 
        } \hfill
        \DatestampYMD{2023}{01}{30}
        \BulletItem
            Developed a GUI for the command line tool called \href{https://www.veripool.org/verilator/}
            {\bfseries Verilator} using \textbf{PyQt}.
        \BulletItem
            Built an installer for Linux using \textbf{cxfreeze} and \textbf{bash} independent of various distros.
        \vspace{5pt}
        
        {\href{https://github.com/pranavkaruvally/PageRankProject}
        {\textbf{\large Analysis of PageRank Algorithm}} 
        (Academic project)
        } \hfill
        \DatestampYMD{2022}{04}{28}
        \BulletItem
            Modeled a sample of the internet using Django and devised a search engine that utilizes the PageRank \\ Algorithm with a team of four.
        \BulletItem
            Analysed the computational complexities of the algorithm.
        \BulletItem
            Examined how graph theory and linear algebra played an important role in the invention of the PageRank Algorithm.
        \vspace{5pt}
        
        {\href{https://github.com/romaljose38/College-project}
        {\textbf{\large PICZA - Social media application}} 
        (Freelance project)
        } \hfill
        \DatestampYMD{2021}{07}{01}
        \BulletItem
            As a team of two, co-created a social media platform for college during pandemic to improve connectivity among students.
        \BulletItem
            Incorporated features such as a low latency chat system powered by websockets, stories, media posts, voice and \\ video calls powered by WebRTC etc.
        \BulletItem
            Wrote the mobile application using Flutter, a cross-platform framework and the backend using Django.
        \BulletItem
            Deployed the application on a Microsoft Azure VPS and performed server load testing using Apache JMeter\newline
            to 90\% of total capacity.

    \section*{ADDITIONAL}
    \hrule \vspace{8pt}
    \textbf{Technical Skills}: Python, Django, PyQt, Flutter, C, Linux, Bash, Git
    \newline
    \textbf{Scholarships}: \textit{INSPIRE SHE Scholarship} | Awarded to students who secured the \textbf{top 1 percentile} in their respective boards in the 12th examination.
    \newline
    \textbf{Activities}: \textit{Technical coordinator} | Association of Students of Computer Applications (ASCA)
    \newline
    \textbf{Achievements}: Secured \textbf{2nd rank} in MCA Entrance examination conducted by LBS
    \newline
    \textbf{Awards}: Winner of All Kerala Inter-Collegiate mathematics quiz | K.E Mannanam (2019) Winner of Inter-Collegiate mathematics quiz | Alphonsa College (2019), First runner-up in ESPOIR: All Kerala Inter-Collegiate mathematics quiz (2023)
    \newline
    \textbf{Certificates}: Discrete Mathematics | NPTEL (Topper), The Joy of Computing using Python | NPTEL (Silver badge), JavaScript Algorithms and Data Structures | FreeCodeCamp
\end{document}